---
title: "Eye size and allometry in deep-sea sergestids"
author: "Katie Thomas"
date: "November 2020"
output:
  html_document:
    code_fold: hide
    theme: flatly
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

<style type="text/css">

body{ /* Normal  */
      font-size: 17px;
  }
  
</style>

```{r setup, include=FALSE}

#set rmarkdown options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.height = 5, fig.width = 8, attr.output='style="max-height: 300px;"') 

#load libraries
library(cowplot)
library(plyr)
library(knitr)
library(kableExtra)
library(gridExtra)
library(evobiR)
library(geiger)
library(phylotools)
library(ape)
library(caper)
library(phytools)
library(smatr)
library(tidyverse)
library(plotly)
```

# Data

## Morphological data

Morphological measurements (eye diameter and body length) were taken from a mixture of fresh and preserved specimens. In total, 459 sergestid specimens were sampled from 16 species belonging to 12 genera and two subgroups (Sergestes and Sergia). Measurements were recorded to ±0.01mm, but we rounded all to the nearest ±0.1mm as we were not confident in the accuracy of such fine measurements taken with calipers on a rocking ship. 

```{r import-data}

# Full specimen morphology dataset  ------

#import data
specimens_raw <- data.frame(read.csv("../Data/specimen_data.csv", header=TRUE, na.strings=c("", "NA", " ", stringsAsFactors = FALSE)))

#tidy data
specimens <- specimens_raw %>%
  mutate(Genus = gsub('\\s+', '', Genus)) %>%
  mutate(Family = str_to_title(Family)) %>%
  mutate(Subgroup = str_to_title(Subgroup)) %>%
  mutate(Genus = str_to_title(Genus)) %>%
  mutate(genus_species = as.factor(paste(Genus, Species, sep = "_"))) %>%
  mutate(pres_bin = recode_factor(Preservation, "ethanol" = "preserved", "paraformaldehyde" = "preserved", "fresh" = "fresh")) %>%
  mutate_if(is.numeric,round, 1)


# Species traits  ------

#import data
traits_raw <- data.frame(read.csv("../Data/species_data.csv", header=TRUE, na.strings=c("", "NA", " ", stringsAsFactors = FALSE)))

#tidy data
traits <- traits_raw %>%
  mutate(Genus = gsub('\\s+', '', Genus)) %>%
  mutate(genus_species = as.factor(paste(Genus, Species, sep = "_"))) %>%
  mutate(Range = Day_Avg - Night_Avg)

# Show sampling -----

#compile number of shrimp sampled by species
counts <-ddply(specimens, .(specimens$Subgroup, specimens$Genus, specimens$Species), nrow) 

#create table column names
names(counts) <- c("Subgroup", "Genus","Species","Sampled") 

#generate scrolling table in RMarkdown
kable(counts[ , c("Subgroup", "Genus","Species","Sampled")], caption = "Species and sampling effort for morphological data from family Sergestidae.") %>% 
                      kable_styling(full_width = F) %>% 
                      collapse_rows(columns = 1, valign = "top") %>%
                      scroll_box(height = "400px") 
```


## Molecular phylogeny

Below is the sergestid molecular phylogeny generated by Charles Golightly. We used _ape_ v.5.4-1 to prune the tree to the 16 species in our dataset and make the tree ultrametric (using the chronopl function with lambda set to 1).

```{r import-phylo, results = "hide"}

#Import phylogeny
tree_orig <- read.tree(file = "../Data/sertestid_tree_rooted")

#Make copy of tree to manipulate
tree_edit <- tree_orig

#Remove locality tags from phylo tip labels 
n <- 3 #which _ to end pattern at
pat <- paste0('^([^_]+(?:_[^_]+){',n-1,'}).*') #pattern
tree_edit$tip.label <- sub(pat, '\\1', tree_edit$tip.label) #remove tags from tips

#Make list of taxa to drop (in tree but not in dataset)
drops <- setdiff(tree_edit$tip.label, as.character(traits$Binomial))

#Drop unwanted tips from phylogeny
tree.pruned <- drop.tip(phy = tree_edit, tip = drops) 

#Check and reorder tree
is.rooted(tree.pruned) 
is.binary.tree(tree.pruned) 
tree <- ladderize(tree.pruned) 

#Make row names of the species the phylogeny tip labels
rownames(traits) <- traits$Binomial

#Reorder species data to match phylogeny order
traits <-ReorderData(tree, traits, taxa.names="row names")

#check that phylogeny tips and data match exactly (if they match will return "OK")
name.check(tree, traits)

#make tree ultrametric
tree <- chronopl(tree, 1)
```

```{r plot-phylo, fig.height=5, fig.width=5}

#plot tree of sampled species with original tip labels
plot.phylo(tree, #phylogeny to plot
           type = "phylogram", #how to visualize phylogeny
           show.tip.label = TRUE, #whether to show tip labels/species names
           cex = 1.0, #text size
           no.margin = TRUE, 
           use.edge.length = TRUE,
           edge.width = 2, #thickness of phylogeny branches
           label.offset = 0.1) #how far away from tips to put labels
```


# Ontogenetic eye-body allometry in Sergestidae

## Eye-body allometry in each species

We first examine ontogenetic eye diameter-body length allometry across 16 species of deep-sea sergestids. Allometric relationships were fit using standardised major axis regression via the _smatr_ v.3.4.8 package. For each species, standard model checks, model fits, and an interactive plot of data and fits are shown. Hover over the plots to see individual data values. Points are colored by the source of the sample (fresh collection or preserved).

Note that for 3 of the species, a large/unreasonable outlier was present. We identified these by eye and they have been removed from the data subsets and analyses, but the outlier value is noted under each species header for reference, and a second plot including the outlier as a red diamond is included for transparency (these can go into the supplemental information if we want). 

```{r pres-cols}
#set colors for fresh and preserved samples
col_pres <- c("ethanol" = "#a6cee3",
              "fresh" = "#b2df8a",
              "paraformaldehyde" = "#1f78b4")
```

### _Allosergestes pectinatus_

```{r dev-apec}

# Subset data -----
apec <- specimens %>% filter(genus_species == "Allosergestes_pectinatus")

# Fit SMA model ------
sma_apec <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = apec, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_apec, which = "default",type = "o") 
plot(sma_apec, which = "residual",type = "o")
plot(sma_apec, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_apec)

#save coefficients of fits as object
cc_sma_apec <- data.frame(coef(sma_apec))

# Make plot ------
plot_apec <- ggplot(apec, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Allosergestes pectinatus") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_apec, aes(intercept = cc_sma_apec[1,1], slope = cc_sma_apec[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_apec[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_apec[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_apec)
```

### _Allosergestes sargassi_

Note: this species has a big outlier that was removed for analyses and plots (eye 0.7, body 13.0). 

```{r dev-asar}

# Subset data -----
#note: outlier removed
asar <- specimens %>% 
  filter(genus_species == "Allosergestes_sargassi") %>%
  filter(!(Eye_Diameter == round(0.67, 1) & Body_Length == round(12.97,1)))

# Fit SMA model ------
sma_asar <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = asar, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_asar, which = "default",type = "o") 
plot(sma_asar, which = "residual",type = "o")
plot(sma_asar, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_asar)

#save coefficients of fits as object
cc_sma_asar <- data.frame(coef(sma_asar))

# Make plot ------
plot_asar <- ggplot(asar, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Allosergestes sargassi") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_asar, aes(intercept = cc_sma_asar[1,1], slope = cc_sma_asar[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_asar[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_asar[1,1], digits = 2), sep = " "), size = 3, col = "black")

#plot with outlier shown
plot_asar_out <- plot_asar +
  geom_point(aes(y=round(0.67, 1), x=round(12.97,1)), colour="red", pch = 18) +
  ggtitle("Allosergestes sargassi + outlier")
  
#plot
ggplotly(plot_asar)

#plot with outlier
ggplotly(plot_asar_out)
```

### _Challengerosergia hansjacobi_

```{r dev-chan}

# Subset data -----
chan <- specimens %>% filter(genus_species == "Challengerosergia_hansjacobi")

# Fit SMA model ------
sma_chan <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = chan, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_chan, which = "default",type = "o") 
plot(sma_chan, which = "residual",type = "o")
plot(sma_chan, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_chan)

#save coefficients of fits as object
cc_sma_chan <- data.frame(coef(sma_chan))

# Make plot ------
plot_chan <- ggplot(chan, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Challengerosergia hansjacobi") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_chan, aes(intercept = cc_sma_chan[1,1], slope = cc_sma_chan[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_chan[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_chan[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_chan)
```

### _Challengerosergia talismani_

```{r dev-ctal}

# Subset data -----
ctal <- specimens %>% filter(genus_species == "Challengerosergia_talismani")

# Fit SMA model ------
sma_ctal <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = ctal, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_ctal, which = "default",type = "o") 
plot(sma_ctal, which = "residual",type = "o")
plot(sma_ctal, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_ctal)

#save coefficients of fits as object
cc_sma_ctal <- data.frame(coef(sma_ctal))

# Make plot ------
plot_ctal <- ggplot(ctal, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Challengerosergia talismani") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_ctal, aes(intercept = cc_sma_ctal[1,1], slope = cc_sma_ctal[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_ctal[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_ctal[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_ctal)
```

### _Deosergestes corniculum_

```{r dev-dcor}

# Subset data -----
dcor <- specimens %>% filter(genus_species == "Deosergestes_corniculum")

# Fit SMA model ------
sma_dcor <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = dcor, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_dcor, which = "default",type = "o") 
plot(sma_dcor, which = "residual",type = "o")
plot(sma_dcor, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_dcor)

#save coefficients of fits as object
cc_sma_dcor <- data.frame(coef(sma_dcor))

# Make plot ------
plot_dcor <- ggplot(dcor, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Deosergestes corniculum") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_dcor, aes(intercept = cc_sma_dcor[1,1], slope = cc_sma_dcor[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_dcor[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_dcor[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_dcor)
```

### _Deosergestes henseni_

```{r dev-dhen}

# Subset data -----
dhen <- specimens %>% filter(genus_species == "Deosergestes_henseni")

# Fit SMA model ------
sma_dhen <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = dhen, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_dhen, which = "default",type = "o") 
plot(sma_dhen, which = "residual",type = "o")
plot(sma_dhen, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_dhen)

#save coefficients of fits as object
cc_sma_dhen <- data.frame(coef(sma_dhen))

# Make plot ------
plot_dhen <- ggplot(dhen, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Deosergestes henseni") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_dhen, aes(intercept = cc_sma_dhen[1,1], slope = cc_sma_dhen[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_dhen[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_dhen[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_dhen)
```

### _Eusergestes arcticus_ 

```{r dev-euar}

# Subset data -----
euar <- specimens %>% filter(genus_species == "Eusergestes_arcticus")

# Fit SMA model ------
sma_euar <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = euar, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_euar, which = "default",type = "o") 
plot(sma_euar, which = "residual",type = "o")
plot(sma_euar, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_euar)

#save coefficients of fits as object
cc_sma_euar <- data.frame(coef(sma_euar))

# Make plot ------
plot_euar <- ggplot(euar, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Eusergestes arcticus") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_euar, aes(intercept = cc_sma_euar[1,1], slope = cc_sma_euar[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_euar[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_euar[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_euar)
```

### _Gardinerosergia splendens_

Note: this species has a big outlier that was removed for analyses and plots (eye 1.7, body 22.0). 

```{r dev-gspl}

# Subset data -----
gspl <- specimens %>% 
  filter(genus_species == "Gardinerosergia_splendens") %>%
  filter(!(Eye_Diameter == round(1.71, 1) & Body_Length == round(21.98,1)))

# Fit SMA model ------
sma_gspl <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = gspl, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_gspl, which = "default",type = "o") 
plot(sma_gspl, which = "residual",type = "o")
plot(sma_gspl, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_gspl)

#save coefficients of fits as object
cc_sma_gspl <- data.frame(coef(sma_gspl))

# Make plot ------
plot_gspl <- ggplot(gspl, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Gardinerosergia splendens") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_gspl, aes(intercept = cc_sma_gspl[1,1], slope = cc_sma_gspl[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_gspl[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_gspl[1,1], digits = 2), sep = " "), size = 3, col = "black")

#plot with outlier shown
plot_gspl_out <- plot_gspl +
  geom_point(aes(y=round(1.71,1), x=round(21.98,1)), colour="red", pch = 18) +
  ggtitle("Gardinerosergia splendens + outlier")
  
#plot
ggplotly(plot_gspl)

#plot with outlier
ggplotly(plot_gspl_out)
```

### _Neosergestes edwardsii_

Note: this species has a big outlier that was removed for analyses and plots (eye 0.9, body 0.7). Also note that for this species, sample size was insufficient to estimate eye-body allometry (N = 6, p = 0.57 for correlation between eye size and body size). 

```{r dev-nedw}

# Subset data -----
nedw <- specimens %>% 
  filter(genus_species == "Neosergestes_edwardsii") %>%
  filter(!(Eye_Diameter == round(0.85,1) & Body_Length == round(0.72,1)))

# Fit SMA model ------
sma_nedw <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = nedw, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_nedw, which = "default",type = "o") 
plot(sma_nedw, which = "residual",type = "o")
plot(sma_nedw, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_nedw)

#save coefficients of fits as object
cc_sma_nedw <- data.frame(coef(sma_nedw))

# Make plot ------
plot_nedw <- ggplot(nedw, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Neosergestes edwardsii") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) 

#plot with outlier shown
plot_nedw_out <- plot_nedw +
  geom_point(aes(x=round(0.85,1), y=round(0.72,1)), colour="red", pch = 18) +
  ggtitle("Neosergestes edwardsii + outlier")
  
#plot
ggplotly(plot_nedw)

#plot with outlier
ggplotly(plot_nedw_out)
```

### _Parasergestes armatus_

```{r dev-parm}

# Subset data -----
parm <- specimens %>% filter(genus_species == "Parasergestes_armatus")

# Fit SMA model ------
sma_parm <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = parm, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_parm, which = "default",type = "o") 
plot(sma_parm, which = "residual",type = "o")
plot(sma_parm, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_parm)

#save coefficients of fits as object
cc_sma_parm <- data.frame(coef(sma_parm))

# Make plot ------
plot_parm <- ggplot(parm, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Parasergestes armatus") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_parm, aes(intercept = cc_sma_parm[1,1], slope = cc_sma_parm[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_parm[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_parm[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_parm)
```

### _Parasergestes vigilax_

```{r dev-pvig}

# Subset data -----
pvig <- specimens %>% filter(genus_species == "Parasergestes_vigilax")

# Fit SMA model ------
sma_pvig <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = pvig, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_pvig, which = "default",type = "o") 
plot(sma_pvig, which = "residual",type = "o")
plot(sma_pvig, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_pvig)

#save coefficients of fits as object
cc_sma_pvig <- data.frame(coef(sma_pvig))

# Make plot ------
plot_pvig <- ggplot(pvig, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Parasergestes vigilax") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_pvig, aes(intercept = cc_sma_pvig[1,1], slope = cc_sma_pvig[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_pvig[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_pvig[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_pvig)
```

### _Phorcosergia grandis_

```{r dev-pgra}

# Subset data -----
pgra <- specimens %>% filter(genus_species == "Phorcosergia_grandis")

# Fit SMA model ------
sma_pgra <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = pgra, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_pgra, which = "default",type = "o") 
plot(sma_pgra, which = "residual",type = "o")
plot(sma_pgra, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_pgra)

#save coefficients of fits as object
cc_sma_pgra <- data.frame(coef(sma_pgra))

# Make plot ------
plot_pgra <- ggplot(pgra, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Phorcosergia grandis") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_pgra, aes(intercept = cc_sma_pgra[1,1], slope = cc_sma_pgra[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_pgra[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_pgra[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_pgra)
```

### _Robustasergia robusta_

```{r dev-rrob}

# Subset data -----
rrob <- specimens %>% filter(genus_species == "Robustasergia_robusta")

# Fit SMA model ------
sma_rrob <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = rrob, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_rrob, which = "default",type = "o") 
plot(sma_rrob, which = "residual",type = "o")
plot(sma_rrob, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_rrob)

#save coefficients of fits as object
cc_sma_rrob <- data.frame(coef(sma_rrob))

# Make plot ------
plot_rrob <- ggplot(rrob, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Robustasergia robusta") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_rrob, aes(intercept = cc_sma_rrob[1,1], slope = cc_sma_rrob[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_rrob[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_rrob[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_rrob)
```

### _Robustosergia regalis_

```{r dev-rreg}

# Subset data -----
rreg <- specimens %>% filter(genus_species == "Robustosergia_regalis")

# Fit SMA model ------
sma_rreg <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = rreg, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_rreg, which = "default",type = "o") 
plot(sma_rreg, which = "residual",type = "o")
plot(sma_rreg, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_rreg)

#save coefficients of fits as object
cc_sma_rreg <- data.frame(coef(sma_rreg))

# Make plot ------
plot_rreg <- ggplot(rreg, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Robustosergia regalis") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_rreg, aes(intercept = cc_sma_rreg[1,1], slope = cc_sma_rreg[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_rreg[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_rreg[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_rreg)
```

### _Sergestes atlanticus_

```{r dev-satl}

# Subset data -----
satl <- specimens %>% filter(genus_species == "Sergestes_atlanticus")

# Fit SMA model ------
sma_satl <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = satl, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_satl, which = "default",type = "o") 
plot(sma_satl, which = "residual",type = "o")
plot(sma_satl, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_satl)

#save coefficients of fits as object
cc_sma_satl <- data.frame(coef(sma_satl))

# Make plot ------
plot_satl <- ggplot(satl, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Sergestes atlanticus") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_satl, aes(intercept = cc_sma_satl[1,1], slope = cc_sma_satl[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_satl[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_satl[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_satl)
```

### _Sergia tenuiremis_

```{r dev-sten}

# Subset data -----
sten <- specimens %>% filter(genus_species == "Sergia_tenuiremis")

# Fit SMA model ------
sma_sten <- sma(formula = Eye_Diameter ~ Body_Length, 
            data = sten, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            alpha = 0.05)

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_sten, which = "default",type = "o") 
plot(sma_sten, which = "residual",type = "o")
plot(sma_sten, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_sten)

#save coefficients of fits as object
cc_sma_sten <- data.frame(coef(sma_sten))

# Make plot ------
plot_sten <- ggplot(sten, aes(x = Body_Length, y = Eye_Diameter, col = Preservation)) + 
  geom_point(size = 2, alpha = 0.8) + 
  scale_color_manual(values = col_pres, name = "Sample state", breaks = c("ethanol", "fresh", "paraformaldehyde")) +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  ggtitle("Sergia tenuiremis") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "italic")) +
  geom_abline(data = cc_sma_sten, aes(intercept = cc_sma_sten[1,1], slope = cc_sma_sten[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_sma_sten[2,1], digits = 2), sep = " "), size = 3, col = "black") +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_sma_sten[1,1], digits = 2), sep = " "), size = 3, col = "black")

ggplotly(plot_sten)
```

### Figure for developmental eye-body scaling across sergestids

```{r figure-dev, fig.width = 10, fig.height = 12, results = "hide"}

#make figure panels
fig.a <- plot_parm + theme(legend.position = "none", axis.title.x = element_blank())
fig.b <- plot_pvig + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.c <- plot_dcor + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.d <- plot_dhen + theme(legend.position = "none", axis.title.x = element_blank())
fig.e <- plot_asar + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.f <- plot_apec + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.g <- plot_chan + theme(legend.position = "none", axis.title.x = element_blank())
fig.h <- plot_ctal + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.i <- plot_pgra + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.j <- plot_sten + theme(legend.position = "none", axis.title.x = element_blank())
fig.k <- plot_rrob + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.l <- plot_rreg + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank())
fig.m <- plot_gspl +theme(legend.position = "none")
fig.n <- plot_satl + theme(legend.position = "none", axis.title.y = element_blank())
fig.o <- plot_euar + theme(legend.position = "none", axis.title.y = element_blank())

# arrange panels in figure
plots <- plot_grid(fig.a, fig.b, fig.c, fig.d, fig.e, fig.f, fig.g, fig.h, fig.i, fig.j, fig.k, fig.l, fig.m, fig.n, fig.o, #list of plots to arrange in grid
           align = 'vh', #align horizontally and vertically
           axis = 'lb',
           labels = c("A", "B", "C", "D", "E", "F", "G", "H", "I","J", "K", "L", "M", "N", "O"), #panel labels for figure
           hjust = -1, #adjustment for panel labels
           nrow = 5) #number of rows in grids

#extract legend
leg <- get_legend(fig.a + theme(legend.position="bottom"))


#view figure
plot_grid(plots, leg, nrow = 2, rel_heights = c(1, .01), align = 'vh')

#export figure
#png("../Figures/dev-allometry.png", width = 10, height = 12, units = "in", res = 500)
pdf("../Figures/dev-allometry.pdf", width = 10, height = 12)
plot_grid(plots, leg, nrow = 2, rel_heights = c(1, .05), align = 'vh')
dev.off()
```

The plots here are scaled to fit the data, so they all look similar but the slopes are actually quite variable and I think pretty interesting. This could be worth exploring for a chunk of the paper, and we might consider examining variation in developmental scaling slopes as a factor of phylogeny and things like whether each species exhibits ontogenetic descent. 

## Test whether species differ in ontogenetic allometry

We've looked at how eyes scale with body size within species, but are there significant differences in ontogenetic allometry across species? The _smatr_ package also allows you to test whether groups exhibit significant differences in allometric scaling (slopes or intercepts). Below, we again use standardized major axis regression to model the scaling of eye diameter with body length across all specimens measured and test whether we see significant differences in ontogenetic scaling across species. This is a bit redundant with above, but will provide statistical evidence of the (very big) difference in slopes among species. 

*Note: As we did not have sufficient sampling to estimate eye-body allometry for _Neosergestes edwardsii_, I've removed it from the specimen dataset before fitting this model.

This test shows that among 15 sergestid species (450 specimens), species significantly differ in their allometric scaling relationships between eye diameter and body length (p < 0.0001). It also yields a table of pairwise comparisons so you can see exactly which species differ significantly in slope and which do not. 

```{r species-smas}

#Remove outliers from specimen dataset
specimens_ed <- specimens %>%
  filter(!(genus_species == "Allosergestes_sargassi" & Eye_Diameter == 0.7 & Body_Length == 13.0)) %>% #(0.67, 12.97 raw)
  filter(!(genus_species == "Gardinerosergia_splendens" & Eye_Diameter == 1.7 & Body_Length == 22.0)) %>% #(1.71, 21.98 raw)
  filter(!(genus_species == "Neosergestes_edwardsii" & Eye_Diameter == 0.8 & Body_Length == 0.7)) #(0.85, 0.72 raw)
  
#Remove Neosergestes edwardsii from dataset for SMA
specimens_sma <- specimens_ed %>%
  filter(genus_species != "Neosergestes_edwardsii") %>%
  mutate(species_text = as.factor(paste(Genus, Species, sep = " "))) # Add labels for species
  
# Model for developmental scaling across specimens grouped by species
sma_species <- sma(formula = Eye_Diameter ~ Body_Length * genus_species, 
            data = specimens_sma, 
            log = "xy", #sets both x and y variables as logged
            method="SMA", #defines SMA as model
            multcomp = TRUE, # adds pairwise comparisons between groups
            multcompmethod = "adjusted", # adjusts p-value for multiple comparisons
            alpha = 0.05) 

#plot fit, residuals, qq
par(mfrow = c(2,2)) #make plot window 2x2
plot(sma_species, which = "default",type = "o") 
plot(sma_species,which = "residual",type = "o")
plot(sma_species, which = "qq", type = "o")
par(mfrow = c(1,1)) 

#view fits
summary(sma_species)

#save coefficients of fits as object
cc_species <- data.frame(coef(sma_species))
```

This figure shows the ontogenetic allometry of all the species with sufficient sampling (n = 15). It's interactive, so you can click on different species in the legend to hide or show those points. That can be helpful for exploring patterns in a big mess of data. To me, it looks a bit like the smaller-bodied species have higher slopes? It looks like _Sergestes atlanticus_, _Allosergestes_pectinatus_, and _Parasergestes vigilax_ have different (higher) slopes compared to the other sergestids, and the other species differ a bit in slopes but more so in intercepts. 

```{r species-fig, fig.width=9, fig.height=9}
#make shape pallette
shapes.sp <- c("Allosergestes pectinatus" = 21,
              "Allosergestes sargassi" = 22, 
              "Challengerosergia hansjacobi" = 23, 
              "Challengerosergia talismani" = 24,
              "Deosergestes corniculum" = 25, 
              "Deosergestes henseni" = 21, 
              "Eusergestes arcticus" = 22,
              "Gardinerosergia splendens" = 23, 
              "Parasergestes armatus" = 24, 
              "Parasergestes vigilax" = 25, 
              "Phorcosergia grandis" = 21, 
              "Robustasergia robusta" = 22,
              "Robustosergia regalis" = 23,
              "Sergestes atlanticus" = 24,
              "Sergia tenuiremis" = 25)

# #make color pallette
# cols.sp <- c("Allosergestes pectinatus" = "#a6cee3",
#               "Allosergestes sargassi" = "#1f78b4", 
#               "Challengerosergia hansjacobi" = "#b2df8a", 
#               "Challengerosergia talismani" = "#33a02c",
#               "Deosergestes corniculum" = "#fb9a99" , 
#               "Deosergestes henseni" = "#e31a1c", 
#               "Eusergestes arcticus" = "#fdbf6f", 
#               "Gardinerosergia splendens" = "#ff7f00", 
#               "Parasergestes armatus" = "#cab2d6", 
#               "Parasergestes vigilax" = "#6a3d9a", 
#               "Phorcosergia grandis" = "gray31" ,
#               "Robustasergia robusta" = "black",
#               "Robustosergia regalis" = "maroon1",
#               "Sergestes atlanticus" = "orchid1",
#               "Sergia tenuiremis" = "burlywood4")

#make color pallette
cols.sp <- c("Allosergestes pectinatus" = "#16ABA8",
              "Allosergestes sargassi" = "#1f78b4", 
              "Challengerosergia hansjacobi" = "#b2df8a", 
              "Challengerosergia talismani" = "#33a02c",
              "Deosergestes corniculum" = "#fb9a99" , 
              "Deosergestes henseni" = "#e31a1c", 
              "Eusergestes arcticus" = "#fdbf6f", 
              "Gardinerosergia splendens" = "#ff7f00", 
              "Parasergestes armatus" = "#cab2d6", 
              "Parasergestes vigilax" = "#6a3d9a", 
              "Phorcosergia grandis" = "gray31" ,
              "Robustasergia robusta" = "burlywood4",
              "Robustosergia regalis" = "maroon1",
              "Sergestes atlanticus" = "orchid1",
              "Sergia tenuiremis" = "black")

#set s limits by species for plots
limits <- specimens_sma %>%
  group_by(genus_species) %>%
  summarise(max = max(Body_Length, na.rm = TRUE),
            min = min(Body_Length, na.rm = TRUE))


#make plot
plot_species <- ggplot(specimens_sma, aes(x = Body_Length, y = Eye_Diameter, color =  species_text, shape = species_text, fill = species_text)) + 
  geom_point(size = 2, alpha = 0.3) + 
  scale_shape_manual(values = shapes.sp, name = "Species") + 
  scale_color_manual(values = cols.sp, name = "Species") +
  scale_fill_manual(values = cols.sp, name = "Species") +
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.text = element_text(face = "italic")) +
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Allosergestes_pectinatus")], xend = limits$max[which(limits$genus_species == "Allosergestes_pectinatus")], y = 10^(log10(limits$min[which(limits$genus_species == "Allosergestes_pectinatus")])*cc_species["Allosergestes_pectinatus", "slope"] + cc_species["Allosergestes_pectinatus", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Allosergestes_pectinatus")])*cc_species["Allosergestes_pectinatus", "slope"] + cc_species["Allosergestes_pectinatus", "elevation"])), color = cols.sp["Allosergestes pectinatus"]) + #Rana temporaria adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Allosergestes_sargassi")], xend = limits$max[which(limits$genus_species == "Allosergestes_sargassi")], y = 10^(log10(limits$min[which(limits$genus_species == "Allosergestes_sargassi")])*cc_species["Allosergestes_sargassi", "slope"] + cc_species["Allosergestes_sargassi", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Allosergestes_sargassi")])*cc_species["Allosergestes_sargassi", "slope"] + cc_species["Allosergestes_sargassi", "elevation"])), color = cols.sp["Allosergestes sargassi"]) + #Allosergestes_sargassi adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Challengerosergia_hansjacobi")], xend = limits$max[which(limits$genus_species == "Challengerosergia_hansjacobi")], y = 10^(log10(limits$min[which(limits$genus_species == "Challengerosergia_hansjacobi")])*cc_species["Challengerosergia_hansjacobi", "slope"] + cc_species["Challengerosergia_hansjacobi", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Challengerosergia_hansjacobi")])*cc_species["Challengerosergia_hansjacobi", "slope"] + cc_species["Challengerosergia_hansjacobi", "elevation"])), color = cols.sp["Challengerosergia hansjacobi"]) + #Challengerosergia_hansjacobi adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Challengerosergia_talismani")], xend = limits$max[which(limits$genus_species == "Challengerosergia_talismani")], y = 10^(log10(limits$min[which(limits$genus_species == "Challengerosergia_talismani")])*cc_species["Challengerosergia_talismani", "slope"] + cc_species["Challengerosergia_talismani", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Challengerosergia_talismani")])*cc_species["Challengerosergia_talismani", "slope"] + cc_species["Challengerosergia_talismani", "elevation"])), color = cols.sp["Challengerosergia talismani"]) + #Challengerosergia_talismani adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Deosergestes_corniculum")], xend = limits$max[which(limits$genus_species == "Deosergestes_corniculum")], y = 10^(log10(limits$min[which(limits$genus_species == "Deosergestes_corniculum")])*cc_species["Deosergestes_corniculum", "slope"] + cc_species["Deosergestes_corniculum", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Deosergestes_corniculum")])*cc_species["Deosergestes_corniculum", "slope"] + cc_species["Deosergestes_corniculum", "elevation"])), color = cols.sp["Deosergestes corniculum"]) + #Deosergestes_corniculum adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Deosergestes_henseni")], xend = limits$max[which(limits$genus_species == "Deosergestes_henseni")], y = 10^(log10(limits$min[which(limits$genus_species == "Deosergestes_henseni")])*cc_species["Deosergestes_henseni", "slope"] + cc_species["Deosergestes_henseni", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Deosergestes_henseni")])*cc_species["Deosergestes_henseni", "slope"] + cc_species["Deosergestes_henseni", "elevation"])), color = cols.sp["Deosergestes henseni"]) + #Deosergestes henseni adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Gardinerosergia_splendens")], xend = limits$max[which(limits$genus_species == "Gardinerosergia_splendens")], y = 10^(log10(limits$min[which(limits$genus_species == "Gardinerosergia_splendens")])*cc_species["Gardinerosergia_splendens", "slope"] + cc_species["Gardinerosergia_splendens", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Gardinerosergia_splendens")])*cc_species["Gardinerosergia_splendens", "slope"] + cc_species["Gardinerosergia_splendens", "elevation"])), color = cols.sp["Gardinerosergia splendens"]) + #Gardinerosergia splendens adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Parasergestes_armatus")], xend = limits$max[which(limits$genus_species == "Parasergestes_armatus")], y = 10^(log10(limits$min[which(limits$genus_species == "Parasergestes_armatus")])*cc_species["Parasergestes_armatus", "slope"] + cc_species["Parasergestes_armatus", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Parasergestes_armatus")])*cc_species["Parasergestes_armatus", "slope"] + cc_species["Parasergestes_armatus", "elevation"])), color = cols.sp["Parasergestes armatus"]) + #Parasergestes armatus adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Parasergestes_vigilax")], xend = limits$max[which(limits$genus_species == "Parasergestes_vigilax")], y = 10^(log10(limits$min[which(limits$genus_species == "Parasergestes_vigilax")])*cc_species["Parasergestes_vigilax", "slope"] + cc_species["Parasergestes_vigilax", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Parasergestes_vigilax")])*cc_species["Parasergestes_vigilax", "slope"] + cc_species["Parasergestes_vigilax", "elevation"])), color = cols.sp["Parasergestes vigilax"]) + #Parasergestes vigilax adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Phorcosergia_grandis")], xend = limits$max[which(limits$genus_species == "Phorcosergia_grandis")], y = 10^(log10(limits$min[which(limits$genus_species == "Phorcosergia_grandis")])*cc_species["Phorcosergia_grandis", "slope"] + cc_species["Phorcosergia_grandis", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Phorcosergia_grandis")])*cc_species["Phorcosergia_grandis", "slope"] + cc_species["Phorcosergia_grandis", "elevation"])), color = cols.sp["Hyla meridiondalis"]) + #Phorcosergia grandis adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Robustasergia_robusta")], xend = limits$max[which(limits$genus_species == "Robustasergia_robusta")], y = 10^(log10(limits$min[which(limits$genus_species == "Robustasergia_robusta")])*cc_species["Robustasergia_robusta", "slope"] + cc_species["Robustasergia_robusta", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Robustasergia_robusta")])*cc_species["Robustasergia_robusta", "slope"] + cc_species["Robustasergia_robusta", "elevation"])), color = cols.sp["Robustasergia robusta"]) + #Robustasergia robusta adult scaling
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Robustosergia_regalis")], xend = limits$max[which(limits$genus_species == "Robustosergia_regalis")], y = 10^(log10(limits$min[which(limits$genus_species == "Robustosergia_regalis")])*cc_species["Robustosergia_regalis", "slope"] + cc_species["Robustosergia_regalis", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Robustosergia_regalis")])*cc_species["Robustosergia_regalis", "slope"] + cc_species["Robustosergia_regalis", "elevation"])), color = cols.sp["Robustosergia regalis"]) +
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Sergestes_atlanticus")], xend = limits$max[which(limits$genus_species == "Sergestes_atlanticus")], y = 10^(log10(limits$min[which(limits$genus_species == "Sergestes_atlanticus")])*cc_species["Sergestes_atlanticus", "slope"] + cc_species["Sergestes_atlanticus", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Sergestes_atlanticus")])*cc_species["Sergestes_atlanticus", "slope"] + cc_species["Sergestes_atlanticus", "elevation"])), color = cols.sp["Sergestes atlanticus"]) +
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Sergia_tenuiremis")], xend = limits$max[which(limits$genus_species == "Sergia_tenuiremis")], y = 10^(log10(limits$min[which(limits$genus_species == "Sergia_tenuiremis")])*cc_species["Sergia_tenuiremis", "slope"] + cc_species["Sergia_tenuiremis", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Sergia_tenuiremis")])*cc_species["Sergia_tenuiremis", "slope"] + cc_species["Sergia_tenuiremis", "elevation"])), color = cols.sp["Sergia tenuiremis"])+
  geom_segment(aes(x = limits$min[which(limits$genus_species == "Eusergestes_arcticus")], xend = limits$max[which(limits$genus_species == "Eusergestes_arcticus")], y = 10^(log10(limits$min[which(limits$genus_species == "Eusergestes_arcticus")])*cc_species["Eusergestes_arcticus", "slope"] + cc_species["Eusergestes_arcticus", "elevation"]), yend = 10^(log10(limits$max[which(limits$genus_species == "Eusergestes_arcticus")])*cc_species["Eusergestes_arcticus", "slope"] + cc_species["Eusergestes_arcticus", "elevation"])), color = cols.sp["Eusergestes arcticus"])


#interactive plot
ggplotly(plot_species)
```

```{r, results = "hide"}
#export figure
#png("../Figures/dev-species.png", width = 12, height = 12, units = "in", res = 500)
pdf("../Figures/dev-species.pdf", width = 9, height = 5)
plot_species
dev.off()
```

## Test for effect of preservation

To test whether preservation type affects eye-body allometry, we have used an additional linear model that includes all specimens after outliers removed (n = 456) and species (n = 15). This model its a fits a regression of eye size vs. body size with both species and preservation type as covariates, and looks for an interaction effect between species and preservation. Specifically, this tests whether preservation type (fresh, ethanol, paraformaldehyde) has an effect on eye size, and whether this differs across species.

```{r pres-smas}

# Model for developmental scaling across specimens * species * preservation
lm_pres <- lm(formula = Eye_Diameter ~ Body_Length * genus_species * Preservation, data = specimens_ed) 

#view anova table (see effects of variables)
anova(lm_pres)
```

The ANOVA table shows that, as we knew, body length, species, and their interaction all have significant effects on eye size (this indicates species-specific patterns of ontogenetic scaling). However, preservation also has a significant effect on eye size (p < 0.0001), as does the interaction between species and preservation (p = 0.007). 

This indicates that we should probably consider preservation error in our analyses, however, since the effect of preservation varies across species and some species have small sample sizes (especially if you break down by preservation type), it is tricky to come up with a correction. My suggestion is that we acknowledge this issue in the results and mention in the discussion how it might affect our interpretations, but also discuss that there does not seem to be a clear, consistent, large-mangnitude effect of preservation across our species data plots. 

## Phylogenetic distribution of allometric slopes

Below, we plot species-specific slopes for developmental eye-body allometry onto the sergestid tree. There is potential to do more with these data; do we have predictions for what might drive species differences in developmental allometry? It looks like body size might be one factor, as the smaller-bodied species seem to have higher slopes. Whether species exhibit ontogenetic descent may be another factor to explore? We might predict that species that have ontogenetic descent and are going into dimmer habitats as they grow may invest in higher eye growth relative to body growth. Do all sergestids exhibit ontogenetic descent? So far, all I've done with these data in an evolutionary framework is test for phylogenetic signal. Let me know if you think of anything else cool to look at! Maybe we could test whether larger body sizes are correlated with lower slopes? Seemed from the plot of all the species that maybe the smaller bodied species had the higher slopes..

```{r slope-phylo, results = "hide", fig.width=10, fig.height=7}

#Add slopes for developmental allometry into species dataframe ----

#add coefficient rownames to genus_species column
cc_species$genus_species <- rownames(cc_species)

#merge coefficients with species data by rowname
species_sma <- left_join(traits, cc_species, by = "genus_species") %>%
  filter(genus_species != "Neosergestes_edwardsii")

# Prep data and phylogeny -----

#Make list of taxa to drop (in tree but not in dataset)
drops <- setdiff(tree$tip.label, as.character(species_sma$Binomial))

#Drop unwanted tips from phylogeny
tree.dev <- drop.tip(phy = tree, tip = drops) 

# Make Genus_species tip labels to replace Binomial codes
sp.tips <- data.frame(old = species_sma$Binomial, new = species_sma$genus_species)

# replace tip labels in phylogeny
tree.dev.plot <- sub.taxa.label(tree.dev, sp.tips)

#change row names of species data
rownames(species_sma) <- species_sma$genus_species

#check that phylogeny and data match exactly
name.check(tree.dev.plot, species_sma)

#resort trait dataset to the order of tree tip labels
species_sma <- species_sma[tree.dev.plot$tip.label, ] 

#make trait vector for slope
slope <- as.vector(species_sma$slope) 

#add tip label names to vector
names(slope) <- species_sma$genus_species

# Phylogeny with slopes for developmental eye-body allometry----
plotTree.wBars(tree.dev.plot, slope, 
               scale = 0.5, 
               tip.labels = TRUE,
               offset = 0.1,
               ftype = "bi",
               fsize = 1)
```

```{r, results = "hide"}
#export figure
#png("../Figures/phylo-slopes.png", width = 10, height = 7, units = "in", res = 500)
pdf("../Figures/phylo-slopes.pdf", width = 10, height = 7)

plotTree.wBars(tree.dev.plot, slope, 
               scale = 0.5, 
               tip.labels = TRUE,
               offset = 0.1,
               ftype = "bi",
               fsize = 1)
dev.off()
```

To test for phylogenetic signal, we fit Pagel's lambda using a maximum likelihood approach in _caper_ v.1.0.1. 

```{r slope-sig}

#fit Pagel's lambda in caper
slopes <- data.frame(slope, names(slope))
mod <- pgls(slope ~ 1, comparative.data(tree.dev.plot, slopes,"names.slope."), lambda="ML")

#summary of model
summary(mod)

#plot likelihood of lambda
plot(pgls.profile(mod, "lambda"))

```

The estimate for Pagel's lambda is 0.77. However, this estimate was not significant, and neither the upper or lower bound of the confidence interval could be estimated. This could indicate that there is no phylogenetic signal in these data, but could also be the result of our sample size of species for comparative evolutionary models (n = 15). Simulations have previously found that estimating Pagel's lambda for datasets of >20 species is problematic and often unreliable (see Freckleton et al., 2002). The likelihood profile of lambda shows that there is increased likelihood that it's somewhere between 0.5 and 1.

# Evolutionary eye-body allometry in Sergestidae

We next examine interspecific (evolutionary) eye-body allometry across sergestids using species means for eye diameter and body length. In calculating species means, we want to use adults only and also make sure that the data we use downstream for traits is relevant to the size class of individuals that we are taking species means from. The biggest concern for the Sergestidae is ontogenetic descent, as this is common across midwater animals and could confound relationships between eye size and depth. However, body size for 'adult' depth distribution data we used in this paper was cutoff between 4-11mm depending on species, and our smallest specimen here is 13 mm, so we are confident that species averages based on full species samples in our dataset are appropriate here. 

Below, we use phylogenetic least-squares regression in _caper_ to fit the allometric relationship between species means for eye size and body length across 16 species of sergestids.

```{r evo-pgls, results = "hide"}

# Prep data ------

#Calculate species means (3 outliers removed)
sp_means <- specimens_ed %>% 
  mutate_if(is.character, as.factor) %>% 
  group_by(genus_species) %>%
  summarise(eye_av = mean(Eye_Diameter), 
            length_av = mean(Body_Length), 
            n = n()) %>%
  ungroup()

#Merge with species trait data stored in dataframe 'species'
species <- traits %>%
  left_join(sp_means, by = "genus_species")

#check that names match in dataframe and tree
name.check(phy = tree, data = species, data.names = species$Binomial)
  
#use caper function to combine phylogeny and data into one object (this function also matches species names in tree and dataset)
species.comp <- comparative.data(data = species, phy = tree, names.col = "Binomial", vcv = TRUE, na.omit = FALSE, warn.dropped = TRUE)

#check for dropped tips or dropped species
species.comp$dropped$tips #phylogeny
species.comp$dropped$unmatched.rows #dataset

# PGLS model -------

#fit model for eye diameter ~ body length
pgls_evo <- pgls(log10(eye_av) ~ log10(length_av), 
               data = species.comp, 
               lambda = "ML", #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_evo)
par(mfrow = c(1, 1))
```

The standard model checks for the PGLS of interspecific eye diameter vs. body length are a bit wonky. The residuals look a little bimodal when they should be normal (though don't have huge weird outliers). We'll have to decide if we're ok with this. Assuming we accept this, model results are below. 

```{r}
#print model output 
summary(pgls_evo)

#save coefficients of fits as object
cc_pgls_evo <- data.frame(coef(pgls_evo))
```

The PGLS regression shows that eyes scale with body length with a slope of 0.82, indicating that eyes have a negative allometry (hypoallometric, slope < 1) with body length. This is what is most common among all vertebrates and some invertebrates that have been examined so far (inverts tend to vary a lot more than verts). 

```{r}

#Likelihood plot for Pagel's lambda 
lambda.evo <- pgls.profile(pgls_evo, "lambda")
plot(lambda.evo, main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

The maximum likelihood estimate of lambda is 1.00 (high phylogenetic signal/Brownian Motion), so that's what _caper_ has used to create the variance-covariance matrix for the regression. However, small sample sizes (< 20-30 data points) have no/little power to estimate lambda (see Freckleton et al. 2002), so tests for phylogenetic signal in this dataset are essentially meaningless (note that the 95% confidence interval for lambda here is 0 to 1, all possible values, and the p-values are non-signficant). For this reason, if any of our other comparative analyses estimate a lambda of 0, we should repeat them again forcing lambda to 1, just so we can see what difference that makes in the model fits (as we can't know what lambda actually is in this small dataset). 

However, if we choose to keep this model, we can plot the model fit onto our data. 

```{r}

# Make plot 
plot_evo <- ggplot(species, aes(x = Body_length, y = Eye_diameter, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.6) + 
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_abline(data = cc_pgls_evo, aes(intercept = cc_pgls_evo[1,1], slope = cc_pgls_evo[2,1])) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 1.5, nudge_x = 4, label = paste("slope =", round(cc_pgls_evo[2,1], digits = 2), sep = " "), size = 3) +
  geom_text(x = -Inf, y = Inf, hjust = -0.05, vjust = 3, label = paste("intercept =", round(cc_pgls_evo[1,1], digits = 2), sep = " "), size = 3)

# Interactive plot
ggplotly(plot_evo)

```

## Bounded extremes of models

With sample sizes too small to generate a robust estimate of lambda, one option is to run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible parameter estimates are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_evo0 <- pgls(log10(eye_av) ~ log10(length_av), 
               data = species.comp, 
               lambda = 0, #set lambda to 0
               bounds=list(lambda=c(0,0)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_evo0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_evo0)

#save coefficients of fits as object
cc_pgls_evo0 <- data.frame(coef(pgls_evo0))

```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals). *Note that when we used a ML estimate of lambda, this was the value used, though the lambda estimate was not significant. 

```{r lambda1}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_evo1 <- pgls(log10(eye_av) ~ log10(length_av), 
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_evo1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_evo1)

#save coefficients of fits as object
cc_pgls_evo1 <- data.frame(coef(pgls_evo1))

```

We can plot both estimates of the relationship between eye size and body size onto our data to see the range of possible fits depending on the true value of lambda. 

```{r, fig.cap = "Eye diameter vs. body length across 16 species of sergesteds. Solid line indicates the PGLS fit when lambda = 0 and dashed line the fit when lambda = 1."}

# Make plot 
plot_evo_bounds <- ggplot(species, aes(x = Body_length, y = Eye_diameter, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.6) + 
  scale_x_log10(name = "Body length (mm)") + #makes x axis log scale and named
  scale_y_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_abline(data = cc_pgls_evo0, aes(intercept = cc_pgls_evo0[1,1], slope = cc_pgls_evo0[2,1]), linetype = "solid") +
  geom_abline(data = cc_pgls_evo1, aes(intercept = cc_pgls_evo1[1,1], slope = cc_pgls_evo1[2,1]), linetype = "dashed")
  

# Interactive plot
ggplotly(plot_evo_bounds)

```

# Correlates of eye size in deep-sea sergestid shrimp

Next, we examine whether variation in eye size is correlated with ecological variables related to light regime and vision: depth and bioluminescent organs. 

## Phylogenetic distribution of eye size and ecology

Here, we examine how absolute and relative eye size vary across the sergestid phylogeny, and the corresponding distribution ecological variables. For visualizing relative eye size, we use the residuals of the PGLS fit for eye-body allometry, as these show eye size corrected for both body size and evolutionary relationships. (Here I have used the model where lambda = 1, as that was the ML estimate despite being non-significant.)

Note: There are few enough species that it would be really nice to put an image of each species next to the phylogeny/associated data if you have them. If not photos, we could make vector images of species silhouettes and scale them by body size. That would look nice and provide some additional useful information on the figure.

```{r eyesize-phylo, results = "hide", fig.width=6, fig.height=4, fig.cap = "Phylogeny of the 15 sertestids sampled depicting absolute eye diameter (purple circles scaled by eye diameter), relative eye investment (bars scaled by the residuals from the PGLS of eye diameter vs. body length, lambda = 1), and photophore complexity (color of bars)."}

#Add residuals from PGLS fits to dataframe ----

#extract pgls residuals 
pglsres <- residuals(pgls_evo) 

#name residuals
colnames(pglsres) <- "pglsres" 

#add rownames to species dataframe
rownames(species) <- species$Binomial

#merge residuals with species data by rowname
species.phy <- merge(species, pglsres, by = "row.names") 

#make column converted to observed eye size as factor of PGLS fit
species.phy$eyefactor <- 10^species.phy$pglsres

# Prep phylogeny -----

# Make Genus_species tip labels to replace Binomial codes
sp.tips <- data.frame(old = species.phy$Binomial, new = species.phy$genus_species)

# replace tip labels in phylogeny
tree.plot <- sub.taxa.label(tree, sp.tips)

# Prep data ----

#change row names of species data
rownames(species.phy) <- species.phy$genus_species

#check that phylogeny and data match exactly
name.check(tree.plot, species.phy)

#resort trait dataset to the order of tree tip labels
species.phy <- species.phy[tree.plot$tip.label, ] 

#make trait vector for absolute eye size
aveye <- as.vector(species.phy$eye_av) 
names(aveye) <- species.phy$genus_species

#make trait vector for eye investment (PGLS residuals)
releye <- as.vector(species.phy$pglsres) #residuals of pgls
names(releye) <- species.phy$genus_species

# Phylogeny with eye size and investment -------

#color vector for photophores
col_ph <- c("lensed" = "palegreen",
            "none" = "honeydew",
            "pesta" = "cadetblue1",
            "unlensed" = "orchid1")

#plot tree with eye investment bars
plotTree.wBars(tree.plot, releye, 
               scale = 1.5, 
               tip.labels = TRUE,
               col = unname(col_ph[as.factor(species.phy$Organ)]),
               offset = 1,
               ftype = "bi",
               fsize = 0.7)

#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add legend for photophores
legend(x = "bottomleft", legend = c("lensed", "none", "pesta", "unlensed"), pch = 22, pt.cex= 2, pt.bg = col_ph, cex = 1, bty = "n", horiz = F)


#Export figure------
pdf("../Figures/phylo.pdf", width = 6, height = 4)

#plot tree with eye investment bars
plotTree.wBars(tree.plot, releye, 
               scale = 1.5, 
               tip.labels = TRUE,
               col = unname(col_ph[species.phy$Organ]),
               offset = 1,
               ftype = "bi",
               fsize = 0.7)

#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add legend for photophores
legend(x = "bottomleft", legend = c("lensed", "none", "pesta", "unlensed"), pch = 22, pt.cex= 2, pt.bg = col_ph, cex = 1, bty = "n", horiz = F)


dev.off()
```

Note: we can (and should) change the colors on this or make BW. We can refine and probably merge with depth distribution phylogeny for a paper figure.

```{r, fig.width=8, fig.height=5.5}

# tree showing day and night mean depths across species

#fix node order upset by ladderization

#filter out internal nodes from second column of edge matrix
is_tip <- tree.plot$edge[,2] <= length(tree.plot$tip.label)
ordered_tips <- tree.plot$edge[is_tip, 2]

#extract tips in right order
#tree.plot$tip.label[ordered_tips]

#resort trait dataset to the order of tree tip labels
species.phy <- species.phy[tree.plot$tip.label[ordered_tips], ] 

#make trait vector for day depth av
day <- as.vector(species.phy$Day_Avg) 
names(day) <- species.phy$genus_species

#make trait vector for night depth av
night <- as.vector(species.phy$Night_Avg) 
names(night) <- species.phy$genus_species

#make trait vector for max reported depth
max <- as.vector(species.phy$Max_reported) 
names(max) <- species.phy$genus_species


#Plot tree with depth ranges
plot(tree.plot, 
     show.tip.label= TRUE, 
     font=3, 
     cex=0.9, 
     label.offset = 0.8, 
     edge.width=2)

#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add gray bar for difference in day/night depths (migration distance)
segments(1.05 + (day*0.0003), 1:length(day), 1.05 + (night*0.0003), 1:length(night), col="gray", lwd=8)

#add yellow point for day depth
segments(1.05 + (day*0.0003), 1:length(day), 1.05 + (day*0.0003), 1:length(day), col="orange", lwd=10)

#add blue point for night depth
segments(1.05 + (night*0.0003), 1:length(night), 1.05 + (night*0.0003), 1:length(night), col="royalblue2", lwd=10)

#add black point for max depth
segments(1.05 + (max*0.0003), 1:length(max), 1.05 + (max*0.0003), 1:length(max), col="black", lwd=7)
```

```{r, results = "hide"}
# export figure 
pdf("../Figures/phylodepth.pdf", width = 8, height = 5.5)

#Plot tree with depth ranges
plot(tree.plot, 
     show.tip.label= TRUE, 
     font=3, 
     cex=0.9, 
     label.offset = 0.8, 
     edge.width=2)

#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add gray bar for difference in day/night depths (migration distance)
segments(1.05 + (day*0.0003), 1:length(day), 1.05 + (night*0.0003), 1:length(night), col="gray", lwd=8)

#add yellow point for day depth
segments(1.05 + (day*0.0003), 1:length(day), 1.05 + (day*0.0003), 1:length(day), col="orange", lwd=10)

#add blue point for night depth
segments(1.05 + (night*0.0003), 1:length(night), 1.05 + (night*0.0003), 1:length(night), col="royalblue2", lwd=10)

#add black point for max depth
segments(1.05 + (max*0.0003), 1:length(max), 1.05 + (max*0.0003), 1:length(max), col="black", lwd=7)

dev.off()

```

The above plot shows absolute eye size (purple dots scaled by eye diameter) and the average daytime (orange) and nighttime (blue) depths for each species in the phylogeny, as well as the maximum reported depth (black). Gray bars indicate vertical distance traveled during diel vertical migrations. Note that this plot is missing a scale bar, easier to add in Illustrator, but minimum depth at night (left/blue points) is 133m and maximum depth during the day (right/orange points) is 1750m. The maximum depth of occurance (black points) across species is 2300m.


## Photophore complexity

**Does eye size correlate with photophore complexity?**

**Prediction:** Eye size may be largest in animals with unlensed photophores, followed by lensed and organ of pesta types, as organs that are visually more difficult to resolve will require greater sensitivity to light (note: should this say longer focal lengths or something like that for higer acuity, not sensitivity?).

### Preliminary plots (photophores)

Before incorporating phylogeny, we can inspect the distribution of our data with boxplots for absolute and relative eye size by photophore type. 

```{r photo-viz}

#Boxplots for absolute eye size across photophores -----
plot_abs_photo <- ggplot(data = species.phy, aes(x = reorder(Organ, eye_av, FUN = mean), y = eye_av, text = genus_species)) + 
  geom_boxplot(notch = FALSE, outlier.shape = NA, alpha = 0.6) + #controls boxes
  stat_summary(fun.y = mean, colour = "black", geom = "point", shape = 18, size = 3, show_guide = FALSE) + #controls what stats shown
 geom_jitter(shape = 19, size = 1.3, alpha = 0.5, position = position_jitter(0.15)) +
  theme(text = element_text(size=14), panel.background = element_blank(), axis.line = element_line(colour = "black")) + #controls background
  xlab("Photophore complexity") +
  ylab("Eye diameter (mm)") +
  ggtitle("Absolute eye size")

ggplotly(plot_abs_photo)

#Boxplots for relative eye investment across photophores -----
plot_rel_photo <- ggplot(data = species.phy, aes(x = reorder(Organ, pglsres, FUN = mean), y = pglsres, text = genus_species)) + 
  geom_boxplot(notch = FALSE, outlier.shape = NA, alpha = 0.6) + #controls boxes
  stat_summary(fun.y = mean, colour = "black", geom = "point", shape = 18, size = 3, show_guide = FALSE) + #controls what stats shown
 geom_jitter(shape = 19, size = 1.3, alpha = 0.5, position = position_jitter(0.15)) +
  theme(text = element_text(size=14), panel.background = element_blank(), axis.line = element_line(colour = "black")) + #controls background
  xlab("Photophore complexity") +
  ylab("Eye ~ body residuals") +
  ggtitle("Relative eye investment")

ggplotly(plot_rel_photo) 
```

It looks like species with organs of pesta tend to have smaller eye diameters and smaller relative eye sizes than species with other types of photophores (note: we may want to combine the non-pesta organs together for power as sample size within groups is really small). We next test this in an evolutionary framework.

### PGLS (photophores)

Below, I run a PGLS model of log10(eye diameter) vs. log10(body length) with photophore complexity as a covariate. Because we have so many states for photophore complexity and a small sample of species, we cannot look at the interaction term for body size x photophore complexity because then our states outnumber our number of observations.

```{r pgls-photo}

#run PGLS modelusing the Maximum Liklihood estimate of lambda
pgls_photo <- pgls(log10(eye_av) ~ log10(length_av) + Organ, 
               data = species.comp, 
               lambda = "ML",
               #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#evaluate model assumptions
par(mfrow = c(2,2)) #makes your plot window into 2x2 panels
plot(pgls_photo) #plot the linear model
par(mfrow = c(1,1)) #set plotting window back to one plot
```

The model checks look pretty good here. 

Next we can take a look at the overall significance of the main, 2-way, 3-way, etc. interactions and sequential sums of squares. Here we can see that body length has a significant effect on eye size (expected, we already knew that), but we also find that photophore complexity/type has a significant effect on eye size when the effect of body size is accounted for (p = 0.01).

```{r}
#anova
anova(pgls_photo)
```

Finally, we look at the PGLS coefficients as well as significance with respect to contrasts. Note that for a categorical variable, R will treat whichever factor comes first as the "control" and will test other factors for significant differences relative to that "control". Here, the comparison state ("control") for photophore complexity is set to "unlensed" (estimate listed under (Intercept) - that's why you don't see that state as a comparison line) and the other states show the *difference* in the estimated intercept for that state compared to the unlensed state, and whether that difference is significant. You can see that "none" and "lensed" show no significant difference in intercept from "unlensed", but that "pesta" does show a significant difference (p = 0.01) and has a lower intercept, indicating smaller relative eye size. 

```{r}
#summary
summary(pgls_photo)
```

The output also includes the maximum-likelihood estimation of lambda, which represents the phylogenetic signal for PGLS model *residuals*. Here, the estimate for lambda is 0.00, which means that there is no phylogenetic signal. This doesn't mean we shouldn't include phylogeny in the model (no reason not to), but it does mean that it's the same result we would get if we assessed this without including phylogeny. This also doesn't mean that there is not phylogenetic signal in the individual traits that we put into the model; this is only lambda for the *model residuals*, not the traits themselves. However, as mentioned above, when you have <20 species the power to estimate lambda is not there, so we may want to consider running these models twice, one forcing lambda to 1 and another forcing lambda to 0, so that we can see how that affects our findings. That could help us in our interpretation (because photophore type is tightly matched to clades, my expectation is that if we force lambda to 0.5 or 1, the relationship may not remain significant.)

```{r}
#Likelihood plot for Pagel's lambda 
plot(pgls.profile(pgls_photo, "lambda"), 
     main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

### Bounded extremes of photophore models

With sample sizes too small to generate a robust estimate of lambda, one option is to run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible parameter estimates are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). *Note that when we used a ML estimate of lambda, this was the value used, though the lambda estimate was not significant. 

```{r lambda0-photo}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_photo0 <- pgls(log10(eye_av) ~ log10(length_av) + Organ, 
               data = species.comp, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_photo0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_photo0)

anova(pgls_photo0)

#save coefficients of fits as object
cc_pgls_photo0 <- data.frame(coef(pgls_photo0))

```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals). 

```{r lambda1-photo}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_photo1 <- pgls(log10(eye_av) ~ log10(length_av) + Organ, 
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_photo1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_photo1)

anova(pgls_photo1)

#save coefficients of fits as object
cc_pgls_photo1 <- data.frame(coef(pgls_photo1))

```

Photophores have a significant effect on eye size when lambda is set to 0 (no phylogenetic signal in model residuals). However, we lose that significance when lambda is set to 1 (high phylogenetic signal in model residuals). While not significant here, it is close (p = 0.075). This means we can’t be totally confident in our finding, as it depends on the true value of lambda (which we can’t estimate with our sample size of species). However, since all patterns we see seem to be driven by organ of pesta, maybe we could try combining categories into organ of pesta or not, for reduced states and more power? I have done that next. 

### Binned models with reduced states for photophores

Here, I've reduced the number of states to the following: bioluminescent with organ of pesta present, bioluminescent with organ of pesta not present, bioluminescence not present. Then I've re-run the models with lambda set to 0 and 1 to see the binned range of potential findings depending on the true value of lambda. 

```{r, results = "hide"}

#recategorize photophore bins
species2 <- species %>%
  mutate(photo2 = recode(Organ, "lensed" = "nonpesta", "unlensed" = "nonpesta"))

#use caper function to combine phylogeny and data into one object (this function also matches species names in tree and dataset)
species.comp2 <- comparative.data(data = species2, phy = tree, names.col = "Binomial", vcv = TRUE, na.omit = FALSE, warn.dropped = TRUE)

#check for dropped tips or dropped species
species.comp2$dropped$tips #phylogeny
species.comp2$dropped$unmatched.rows #dataset

```

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0-photobin}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_photo0_bin <- pgls(log10(eye_av) ~ log10(length_av) + photo2, 
               data = species.comp2, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_photo0_bin)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_photo0_bin)

anova(pgls_photo0_bin)

```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals). 

```{r lambda1-photobin}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_photo1_bin <- pgls(log10(eye_av) ~ log10(length_av) + photo2, 
               data = species.comp2, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_photo1_bin)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_photo1_bin)

anova(pgls_photo1_bin)

```

Here when we bin into 3 groups for photophores (organ of pesta, no organ of pesta, no photophores at all), we find that organ type has a significant effect on eye size in both models (lambda = 1 and lambda = 0). This is a robust result, as whatever the true value of lambda is, the association should hold. The only caveat I will add to this is that since we only have a single evolutionary transition from organ of pesta to non organ of pesta represented in our dataset, the association would be more convincing if found later across larger samples/trees/etc (just something small to mention in discussion). 

## Depth distributions

**Does eye size correlate with daytime or nighttime depth distributions? Are these relationships affected by vertical migration?**

**Prediction:** Eye size increases with daytime depth, as these animals may require the greatest sensitivity to light to cope with the exponential attenuation of light with depth. 

Note: Did we have predictions about how vertical migration (which we are factoring in as the interaction effect of day and night depths) might affect eye size? I might predict that stronger migrators might have larger eyes, as they may be able to use ambient light for vision more of the time (things that stay deep at night would not have ambient light available at night). Or they might be using their eyes to follow an isolume. Just a couple ideas!

### Exploratory plots (depth)

Before incorporating phylogeny, we can inspect the distribution of our data with scatter plots for absolute and relative eye size and body size vs. daytime and nighttime depth. In the below interactive plots, daytime depths are orange and nighttime depths are blue. Maximum reported depths are in black squares. 

```{r depth-viz}

# Absolute eye size with depths ------
plot_abs_depths <- ggplot(species.phy, aes(x = eye_av, y = Day_Avg, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.8, col = "orange") + 
  scale_y_reverse(name = "Depth (m)") + #makes x axis log scale and named
  scale_x_log10(name = "Eye diameter (mm)") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_point(aes(x = eye_av, y = Night_Avg), size = 2, alpha = 0.8, col = "royalblue2") +
  geom_point(aes(x = eye_av, y = Max_reported), size = 1.5, alpha = 0.8, pch = 15, col = "black")

ggplotly(plot_abs_depths)

# Absolute eye size with depths ------
plot_length_depths <- ggplot(species.phy, aes(x = length_av, y = Day_Avg, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.8, col = "orange") + 
  scale_y_reverse(name = "Depth (m)") + #makes x axis log scale and named
  scale_x_log10(name = "Body length (mm)") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_point(aes(x = length_av, y = Night_Avg), size = 2, alpha = 0.8, col = "royalblue2")+
  geom_point(aes(x = length_av, y = Max_reported), size = 1.5, alpha = 0.8, pch = 15, col = "black")

ggplotly(plot_length_depths)

# Eye size/body size with max depth -----
plot_rel_depth <- ggplot(species.phy, aes(x = eye_av/length_av, y = Day_Avg, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.8, col = "orange") + 
  scale_y_reverse(name = "Depth (m)") + #makes x axis log scale and named
  scale_x_log10(name = "Eye/body ratio") + #makes y axis log scale and named
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_point(aes(x = eye_av/length_av, y = Night_Avg), size = 2, alpha = 0.8, col = "royalblue2") +
  geom_point(aes(x = eye_av/length_av, y = Max_reported), size = 1.5, alpha = 0.8, pch = 15, col = "black")

ggplotly(plot_rel_depth)

#is daytime depth correlated with maximum depth?
plot_daymax <- ggplot(species.phy, aes(x = Day_Avg, y = Max_reported, text = genus_species)) + 
  geom_point(size = 2, alpha = 0.8, col = "black") + 
  ylab("Max reported depth (m)") + 
  xlab("Daytime mean depth (m)") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggplotly(plot_daymax)
```

Visual inspection of the data shows that absolute eye size, body size, and relative eye size maybe could seem to increase with daytime depth, but if so it's only driven by a couple of data points. Nighttime depth doesn't vary much across species, but to me it looks like the species with larger body sizes might also have the larger differences between nighttime and daytime depths. Maximum reported depth shows a similar pattern to daytime depth. We next test this in an evolutionary framework.


### PGLS (mean depths)

Below, I run a PGLS model of log10(eye diameter) vs. log10(body length) with covariates of log10(daytime depth), log10(nighttime depth), and the interaction between daytime and nighttime depth.

```{r pgls-depth}

#run PGLS model using the Maximum Liklihood estimate of lambda
pgls_depth <- pgls(log10(eye_av) ~ log10(length_av)  + log10(Day_Avg) * log10(Night_Avg), 
               data = species.comp, 
               lambda = "ML", bounds = list(lambda = c(1e-05, 1)),
               #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#evaluate model assumptions
par(mfrow = c(2,2)) #makes your plot window into 2x2 panels
plot(pgls_depth) #plot the linear model
par(mfrow = c(1,1)) #set plotting window back to one plot
```

The model checks here look a bit weird (residuals look bimodal; assumption is normality). 

Next we can take a look at the overall significance of the main effects/interactions and sequential sums of squares. Here we can see that body length has a significant effect on eye size when depth is corrected for (expected, and we already knew that), but daytime depth, nighttime depth, and the interaction between daytime and nighttime depth do not have significant effects on eye size. 

```{r}
#anova
anova(pgls_depth)
```

Finally, we look at the PGLS coefficients as well significance with respect to contrasts. 

```{r}
#summary
summary(pgls_depth)
```

The output also gives a maximum-likelihood estimation of lambda = 1.00, indicating that there is high phylogenetic signal in the residuals of the model (and that _caper_ used a lambda of 1 to set the variance-covariance matrix in the regression). However, small sample sizes have no power to estimate the true value of lambda, so this is not very meaningful in this dataset. We should decide on a strategy for analysis (as mentioned above, may want to run all models again with lambda fixed at 0 as a comparison for the supp info so we can discuss how that affects our results).

```{r}
#Likelihood plot for Pagel's lambda 
plot(pgls.profile(pgls_depth, "lambda"), 
     main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

### Bounded extremes of mean depth models

With sample sizes too small to generate a robust estimate of lambda, we here again run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible parameter estimates are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0-depth}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_depth0 <- pgls(log10(eye_av) ~ log10(length_av) + log10(Day_Avg) * log10(Night_Avg),
               data = species.comp, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_depth0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_depth0)

anova(pgls_depth0)
```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals). *Note that when we used a ML estimate of lambda, this was the value used, though the lambda estimate was not significant. 

```{r lambda1-depth}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_depth1 <- pgls(log10(eye_av) ~ log10(length_av) + log10(Day_Avg) * log10(Night_Avg),
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_depth1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_depth1)

anova(pgls_depth1)
```

In both models bounding the possible true value of lambda, daytime depth, nighttime depth, and the interaction between day and night depths do not have significant effects on eye size in these species. This means that our finding is robust, regardless of our challenge estimating phylogenetic signal in our model residuals. 

## Maximum depth

While we found no association between eye size and mean daytime or nighttime depths, we can also test eye size vs. the maximum reported depth for each species. 

### PGLS (max depth)

Below, I run a PGLS model of log10(eye diameter) vs. log10(body length) with covariate of maximum depth.

```{r pgls-maxdepth}

#run PGLS model using the Maximum Liklihood estimate of lambda
pgls_maxdepth <- pgls(log10(eye_av) ~ log10(length_av)  + log10(Max_reported), 
               data = species.comp, 
               lambda = "ML", bounds = list(lambda = c(1e-05, 1)),
               #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#evaluate model assumptions
par(mfrow = c(2,2)) #makes your plot window into 2x2 panels
plot(pgls_maxdepth) #plot the linear model
par(mfrow = c(1,1)) #set plotting window back to one plot
```

The model checks here look good.

Next we can take a look at the overall significance of the main effects/interactions and sequential sums of squares. Here we can see that body length has a significant effect on eye size when maximum reported depth is corrected for (expected, and we already knew that), but that maximum depth does not have a significant effect on eye size. 

```{r}
#anova
anova(pgls_maxdepth)
```

Finally, we look at the PGLS coefficients as well significance with respect to contrasts. 

```{r}
#summary
summary(pgls_maxdepth)
```

The output also gives a maximum-likelihood estimation of lambda = 0.93, indicating that there is high phylogenetic signal in the residuals of the model (and that _caper_ used a lambda of 0.93 to set the variance-covariance matrix in the regression). However, small sample sizes have no power to estimate the true value of lambda, so this is not very meaningful in this dataset. We additionally run models with lambda fixed at 0 and at 1 as comparisons for the supp info so we can discuss how that affects our results.

```{r}
#Likelihood plot for Pagel's lambda 
plot(pgls.profile(pgls_maxdepth, "lambda"), 
     main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

### Bounded extremes of maximum reported depth models

With sample sizes too small to generate a robust estimate of lambda, we here run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible results are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0-maxdepth}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_maxdepth0 <- pgls(log10(eye_av) ~ log10(length_av) + log10(Max_reported),
               data = species.comp, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_maxdepth0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_maxdepth0)

anova(pgls_maxdepth0)
```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals).

```{r lambda1-maxdepth}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_maxdepth1 <- pgls(log10(eye_av) ~ log10(length_av) + log10(Max_reported),
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_maxdepth1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_maxdepth1)

anova(pgls_maxdepth1)
```

In both models bounding the possible true value of lambda, maximum depth does not have significant effects on eye size in these species.


## Depth range traversed in DVM (nighttime mean - daytime mean)

While we found no association between eye size and mean daytime or nighttime depths or the interaction between them, I also wanted to check whether there was an association between eye size and the distance traversed during DVM. 

### PGLS (range traversed)

Below, I run a PGLS model of log10(eye diameter) vs. log10(body length) with covariate of depth range traversed during DVM.

```{r pgls-depthrange}

#run PGLS model using the Maximum Liklihood estimate of lambda
pgls_depthrange <- pgls(log10(eye_av) ~ log10(length_av)  + Range, 
               data = species.comp, 
               lambda = "ML", bounds = list(lambda = c(1e-05, 1)),
               #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#evaluate model assumptions
par(mfrow = c(2,2)) #makes your plot window into 2x2 panels
plot(pgls_depthrange) #plot the linear model
par(mfrow = c(1,1)) #set plotting window back to one plot
```

The model checks here look a bit wonky.

Next we can take a look at the overall significance of the main effects/interactions and sequential sums of squares. Here we can see that body length has a significant effect on eye size when depth range is corrected for (expected, and we already knew that), but that depth range does not have a significant effect on eye size. 

```{r}
#anova
anova(pgls_depthrange)
```

Finally, we look at the PGLS coefficients as well significance with respect to contrasts. 

```{r}
#summary
summary(pgls_depthrange)
```

The output also gives a maximum-likelihood estimation of lambda = 1, indicating that there is high phylogenetic signal in the residuals of the model (and that _caper_ used a lambda of 1 to set the variance-covariance matrix in the regression). However, small sample sizes have no power to estimate the true value of lambda, so this is not very meaningful in this dataset. We additionally run models with lambda fixed at 0 and at 1 as comparisons for the supp info so we can discuss how that affects our results.

```{r}
#Likelihood plot for Pagel's lambda 
plot(pgls.profile(pgls_depthrange, "lambda"), 
     main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

### Bounded extremes of depth range models

With sample sizes too small to generate a robust estimate of lambda, we here run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible results are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0-depthrange}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_depthrange0 <- pgls(log10(eye_av) ~ log10(length_av) + Range,
               data = species.comp, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_depthrange0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_depthrange0)

anova(pgls_depthrange0)
```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals).

```{r lambda1-depthrange}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_depthrange1 <- pgls(log10(eye_av) ~ log10(length_av) + Range,
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_depthrange1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_depthrange1)

anova(pgls_depthrange1)
```

In both models bounding the possible true value of lambda, depth range does not have significant effects on eye size in these species.


## Habitat

### Preliminary plots (habitat)

Before incorporating phylogeny, we can inspect the distribution of our data with boxplots for absolute and relative eye size bye habitat. 

```{r photo-viz-eco}

# Phylogeny with eye size and investment and ecology -------

#color vector for photophores
col_eco <- c("no" = "#7FDBFF",
            "yes" = "#FF851B")

#resort trait dataset to the order of tree tip labels
species.phy <- species.phy[tree.plot$tip.label, ] 

#plot tree with eye investment bars
plotTree.wBars(tree.plot, releye, 
               scale = 1.5, 
               tip.labels = TRUE,
               col = unname(col_eco[as.factor(species.phy$Benthopelagic)]),
               offset = 1,
               ftype = "bi",
               fsize = 0.7)

#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add legend for photophores
legend(x = "bottomleft", legend = c("pelagic", "benthopelagic"), pch = 22, pt.cex= 2, pt.bg = col_eco, cex = 1, bty = "n", horiz = F)


#Boxplots for absolute eye size across photophores -----
plot_abs_eco <- ggplot(data = species.phy, aes(x = reorder(Benthopelagic, eye_av, FUN = mean), y = eye_av)) + 
  geom_boxplot(notch = FALSE, outlier.shape = NA, alpha = 0.6) + #controls boxes
  stat_summary(fun.y = mean, colour = "black", geom = "point", shape = 18, size = 3, show_guide = FALSE) + #controls what stats shown
 geom_jitter(shape = 19, size = 1.3, alpha = 0.5, position = position_jitter(0.15)) +
  theme(text = element_text(size=14), panel.background = element_blank(), axis.line = element_line(colour = "black")) + #controls background
  xlab("Benthopelagic") +
  ylab("Eye diameter (mm)") +
  ggtitle("Absolute eye size")

ggplotly(plot_abs_eco)

#Boxplots for relative eye investment across photophores -----
plot_rel_eco <- ggplot(data = species.phy, aes(x = reorder(Benthopelagic, pglsres, FUN = mean), y = pglsres)) + 
  geom_boxplot(notch = FALSE, outlier.shape = NA, alpha = 0.6) + #controls boxes
  stat_summary(fun.y = mean, colour = "black", geom = "point", shape = 18, size = 3, show_guide = FALSE) + #controls what stats shown
 geom_jitter(shape = 19, size = 1.3, alpha = 0.5, position = position_jitter(0.15)) +
  theme(text = element_text(size=14), panel.background = element_blank(), axis.line = element_line(colour = "black")) + #controls background
  xlab("Benthopelagic") +
  ylab("Eye ~ body residuals") +
  ggtitle("Relative eye investment")

ggplotly(plot_rel_eco) 
```

```{r, results = "hide"}
#Export figure------
pdf("../Figures/phylo_eco.pdf", width = 6, height = 4)

#plot tree with eye investment bars
plotTree.wBars(tree.plot, releye, 
               scale = 1.5, 
               tip.labels = TRUE,
               col = unname(col_eco[as.factor(species.phy$Benthopelagic)]),
               offset = 1,
               ftype = "bi",
               fsize = 0.7)


#add tip labels for absolute eye size
tiplabels(cex = 1.5*aveye,
          pch = 19, #shape of labels
          col = "mediumpurple",
          offset = 0)

#add legend for ecology
legend(x = "bottomleft", legend = c("pelagic", "benthopelagic"), pch = 22, pt.cex= 2, pt.bg = col_eco, cex = 1, bty = "n", horiz = F)

dev.off()
```

It looks like benthopelagic species have big-ish eyes, but it's small sample size so hard to say. Distribution overlaps with pelagic species. We next test this in an evolutionary framework.

### PGLS (ecology)

Below, I run a PGLS model of log10(eye diameter) vs. log10(body length) with ecology (benthopelagic vs. pelagic) as a covariate.

```{r pgls-eco}

#run PGLS modelusing the Maximum Liklihood estimate of lambda
pgls_eco <- pgls(log10(eye_av) ~ log10(length_av) + Benthopelagic, 
               data = species.comp, 
               lambda = "ML",
               #uses Maximum Liklihood estimate of lambda
               param.CI = 0.95)

#evaluate model assumptions
par(mfrow = c(2,2)) #makes your plot window into 2x2 panels
plot(pgls_eco) #plot the linear model
par(mfrow = c(1,1)) #set plotting window back to one plot
```

Next we can take a look at the overall significance of the main, 2-way, 3-way, etc. interactions and sequential sums of squares. Here we can see that body length has a significant effect on eye size (expected, we already knew that), but ecology (benthopelagic or not) has no effect on eye size (p = 0.57). 

```{r}
#anova
anova(pgls_eco)
```

Finally, we look at the PGLS coefficients as well as significance with respect to contrasts. 

```{r}
#summary
summary(pgls_eco)
```

The output also includes the maximum-likelihood estimation of lambda, which represents the phylogenetic signal for PGLS model *residuals*. Here, the estimate for lambda is 1.00, which means that there is the highest phylogenetic signal. However, as mentioned above, when you have <20 species the power to estimate lambda is not there, so below we will run models with the min and max possible values of lambda to see how that affects our results. 

```{r}
#Likelihood plot for Pagel's lambda 
plot(pgls.profile(pgls_eco, "lambda"), 
     main = "Pagel's lambda", 
     sub = "Solid red line indicates estimate for lambda and broken red lines indcaite the 95% confidence interval")

```

### Bounded extremes of ecology models

With sample sizes too small to generate a robust estimate of lambda, one option is to run models with the lowest and possible bounds of lambda (0 and 1), so that we can see what the range of possible parameter estimates are depending on the phylogenetic signal of the model residuals. Below, we fit these two models so that we can compare them. 

Here is the model fit with lambda fixed at 0 (no phylogenetic signal in model residuals). 

```{r lambda0-eco}

#fit model for eye diameter ~ body length (lambda = 0)
pgls_eco0 <- pgls(log10(eye_av) ~ log10(length_av) + Benthopelagic, 
               data = species.comp, 
               lambda = 0.00001, #set lambda to 0
               bounds=list(lambda=c(0.00001,0.00001)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_eco0)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_eco0)

anova(pgls_eco0)
```

Here is the model fit with lambda fixed at 1 (highest phylogenetic signal in model residuals). *Note that when we used a ML estimate of lambda, this was the value used, though the lambda estimate was not significant. 

```{r lambda1-eco}

#fit model for eye diameter ~ body length (lambda = 1)
pgls_eco1 <- pgls(log10(eye_av) ~ log10(length_av) + Benthopelagic, 
               data = species.comp, 
               lambda = 1, #set lambda to 1
               bounds=list(lambda=c(1,1)),
               param.CI = 0.95)

#check model assumptions
par(mar = c(4,4,2,2))
par(mfrow = c(2, 2))
plot(pgls_eco1)
par(mfrow = c(1, 1))

#parameter estimates
summary(pgls_eco1)

anova(pgls_eco1)


```

Ecology (benthopelagic/pelagic) does not have a significant effect on eye size when lambda is set to 0 or 1. Thus, our finding is robust whatever the true value of lambda is. However, with n = 3 for benthopelagic species, this was probably not a sufficient sample size to detect any patterns that may exist. 

